\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}

\input{../Comments}
\input{../Common}

\title{User Guide\\\progname}

\author{\authname}

\date{}

\begin{document}

\maketitle
\newpage


\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
April 5, 2023 & Jordan B & Added User Guide\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\section{Instructions}
\textbf{Step 1}: Ensure that the device is powered on by activating the switch on the side of the device. This should be reflected by a green light on the top of the device.
\newline
\textbf{Step 2}: Open the application and hit allow on the prompted accessibility.
\newline
\textbf{Step 3}: You will be prompted with a welcome page; click the homepage button.
\newline
\textbf{Step 4}: The homepage has two buttons keyword selection and pairing; click the pairing button.
\newline
\textbf{Step 5}: The pairing page will automatically find the nearby device and text will show that it has found a device.
\newline
\textbf{Step 6}: Click the connect button found on the bottom of the page and wait.
\newline
\textbf{Step 7}: The application will say “Connecting..” and the device will have a blue light come on.
\newline
\textbf{Step 8}: The application says that the device is connected.
\newline
\textbf{Step 9}: Hit the back button in the top left corner of the screen; this will take you back to the home page.
\newline
\textbf{Step 10}: Click on the keyword selection button on the bottom of the screen.
\newline
\textbf{Step 11}: The keyword selection screen should pop up and you will see a list of available keywords and a drop down for confidence levels.
\newline
\textbf{Step 12}: choose the desired keywords that you want to be classified by clicking on the switch. The switch will turn green when the keyword is activated.
\newline
\textbf{Step 13}: By clicking the drop down in the top of the screen you can choose a value for the confidence level that you would prefer. 
\newline
\textbf{Step 14}: You can now use the device as intended and it will react to the chosen keywords.
\newline
\textbf{Step 15}: You can now click the back button on the top left of the screen to return to the home page.
\newline
\textbf{Step 16}: By returning to the pairing page you will see an activated button that says “Disconnect” you may click this when you are done using the device.
\newline

\section{Resources}
Please refer to video provided for further detail. 

\end{document}